---
title: "SPYTrade v1.1"
author: "Akbar Rizqiansyah"
date: "06/11/2021"
output: html_document
---
bla bla bla
abc123
absadasdsadsf

Objective:
Do proper out of sample forecasting (5 days), see how the model performs along the 5 days.
Also make the whole dataframe tidier, make it so it can handle more than 2 assets.
Actively delete unused objects and variables to save on memory.
Extension: look into multi path forecasting + data assimilation to combine the different estimates.

Difference to v2.5.2:
No LSTM estimates at the end

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
EVAL_GARCH_OPTION = FALSE
```

```{r}
library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)
library(xts)
library(tidyverse)
library(tidyquant)
library(visdat)
```

# 1.0 Data tidying
Download the data
```{r, warning = FALSE, echo = FALSE}
#Download data
ticker = c("AAPL",
           "AMZN",
           "MSFT",
           "NKE",
           "WMT",
           "WST",
           "MA",
           "LMT",
           "RTX",
           "REGN")
all_stock <- tq_get(ticker,
              from = "2019-11-01",
              to = "2021-11-01",
              get = "stock.prices") %>%
  select(symbol, date, close) %>%
  mutate(lret = c(0, diff(log(close))))

#Turn all first days returns to 0
first_day <- all_stock %>%
  group_by(symbol) %>%
  summarise(date = min(date)) %>%
  left_join(all_stock, by = c("symbol" = "symbol", "date" = "date")) %>%
  mutate(lret = 0)

all_stock <- all_stock %>% 
  anti_join(first_day, by = c("symbol" = "symbol", "date" = "date")) %>%
  bind_rows(first_day) %>%
  arrange(date)

#Delete objects
rm(first_day)
```

Split the data into training and verification data
2/3 training, 1/3 training
```{r}
#Split the data into its individual symbols
all_stock_lret <- pivot_wider(all_stock,
                              id_cols = date,
                              names_from = symbol,
                              values_from = lret,
                              names_glue = "{symbol}.lret")
all_stock_close <- pivot_wider(all_stock,
                               id_cols = date,
                               names_from = symbol,
                               values_from = close,
                               names_glue = "{symbol}.close")

all_stock <- all_stock_lret %>% 
  full_join(all_stock_close, by ="date")

#Remove 1/3 amount of observations for verification later
N_TRAIN = ceiling(nrow(all_stock_lret)*2/3)
N_VERIFICATION = nrow(all_stock_lret) - N_TRAIN

all_stock_train <- all_stock %>%
  head(N_TRAIN)

all_stock_verification <- all_stock %>%
  tail(N_VERIFICATION)

#Delete objects
rm(all_stock_lret, all_stock_close)
```

Check for any missing data
```{r}
vis_miss(all_stock %>% select(ends_with(".lret")))
vis_miss(all_stock %>% select(ends_with(".close")))
```
See correlation
See both Pearson's and Spearman's (Assuming no normal dependencies)
```{r}
library(ggcorrplot)
ggcorrplot(cor(all_stock%>%select(ends_with(".lret")), method = "pearson"), lab=TRUE)
ggcorrplot(cor(all_stock%>%select(ends_with(".lret")), method = "spearman"), lab=TRUE)
```
Let's stick with AMZN and MSFT first, then generalise if possible
```{r}
select_ticker = c("AMZN", "MSFT", "AAPL", "RTX", "WMT")

all_stock <- all_stock %>%
  select(date, starts_with(select_ticker))
all_stock_train <- all_stock_train %>%
  select(date, starts_with(select_ticker))
all_stock_verification <- all_stock_verification %>%
  select(date, starts_with(select_ticker))

ticker = select_ticker
```

# 2.0 Fit into ARIMA-eGARCH model
```{r}
#Find best fit ARIMA and GARCH (Asymmetric) specification for all stocks
best_fit <- tibble(symbol = ticker,
               ARIMA_AIC = Inf,
               GARCH_AIC = Inf,
               ARIMA_p = 1,
               ARIMA_d = 0,
               ARIMA_q = 1,
               GARCH_p = 1,
               GARCH_q = 1,
               spec = list(0),
               final_fit = list(0)) %>%
  nest(order = c(ARIMA_p, ARIMA_d, ARIMA_q, GARCH_p, GARCH_q))
```


# Find best ARIMA-GARCH model based on AIC
Note 16/11/2021 - 
Sometimes ugarchfit() fails to converge (example is AAPL data) for the best ARIMA lags, but converges for lower ARIMA lags. Maybe need to temporarily store the AIC of all ARIMA model, and walk backward the ARIMA model from best to worse AIC if GARCH fails to converge

```{r, eval = EVAL_GARCH_OPTION}
library(timetk)

#Settings
ERR_DIST = "std" #norm, snorm, std, sstd, ged, sged
MAX_ARIMA_P = 5
MAX_ARIMA_Q = 5
MAX_GARCH_P = 5
MAX_GARCH_Q = 5
n=0

for (i in ticker) {
  n = n + 1
  #Temporary variables
  current.symbol <- i
  #Convert to XTS object to maintain date consistencies
  df_xts <- tk_xts(all_stock_train,
                   select = paste(current.symbol, ".lret", sep =""),
                   date_var = "date")
  
  #Temporary dataframe to store the results for all ARIMA
  #Will not store ARIMA results that are problematic
  df_arima_results <- tibble(p=0,
                             d=0,
                             q=0,
                             AIC = Inf)
  
  

  for (p in 0:MAX_ARIMA_P) for (q in 0:MAX_ARIMA_Q) {
    if ( p == 0 && q == 0) {
      next
    }
    arimaFit = tryCatch( arima(df_xts, order=c(p, 0, q)),
                         error=function( err ) {
                           message(err)
                           return(FALSE)
                         },
                         warning=function( err ) {
                           # message(err)
                           return(FALSE)
                         } )

    if( !is.logical( arimaFit ) ) {
      df_arima_results <- df_arima_results %>%
        bind_rows(tibble(p = p,
                         d = 0,
                         q = q,
                         AIC = AIC(arimaFit)))
    } else {
      next
    }
  }
  
  #Sort the results based on the best AIC
  df_arima_results <- df_arima_results %>%
    arrange(AIC)
  
  #Fit GARCH specification
  #Move down the best AIC table if no solution can be found for all lags
  final.aic <- Inf
  m = 0
  while (final.aic == Inf & m < nrow(df_arima_results)){
    #Move down the best AIC table if no solution can be found for all lags
    m = m + 1
    final.aic <- Inf
    ARIMA_p <- df_arima_results$p[m]
    ARIMA_d <- df_arima_results$d[m]
    ARIMA_q <- df_arima_results$q[m]
    final.garchOrder <- c(0,0)
    
    for (p in 1:MAX_GARCH_P) for (q in 1:MAX_GARCH_Q) {
      print(paste("Stock =", current.symbol, 
                  "ARIMA p =", ARIMA_p,
                  "ARIMA d =", ARIMA_d,
                  "ARIMA q =", ARIMA_q,
                  "GARCH p =", p,
                  "GARCH q =", q))
      spec = ugarchspec(
        variance.model=list(model ="eGARCH",
                            #submodel = "TGARCH",
                            garchOrder=c(p,q)),
        mean.model=list(armaOrder=c(ARIMA_p,
                                    ARIMA_q),
                                    include.mean=T),
        distribution.model= ERR_DIST
      )
      garchFit = tryCatch(
        ugarchfit(
          spec, df_xts, solver = 'hybrid'
        ),
        error=function( err ) {
                             message(err)
                             return(FALSE)
                           },
        warning=function( err ) {
                             #message(err)
                             return(FALSE)
                           } )
  
      if( !is.logical( garchFit ) ) {
        current.aic <- infocriteria(garchFit)[1]
        if (current.aic < final.aic) {
          final.aic <- current.aic
          final.garchOrder <- c(p, q)
          final.garch.spec <- spec
          final.garch.fit <- garchFit
        }
      } else {
        next
      }
    }
    if (final.aic == Inf){
      print(paste("No GARCH specification found for stock",
                  current.symbol,
                  "ARIMA(",
                  p, ", ", d, ", ", q, ")"))
    }
  }
  
  #Throw an error if no GARCH specification could be found with all valid ARIMA models
  if (final.aic == Inf){
    message("ERR: No GARCH specification can be found")
  }
  
  #Store the results
  #Store the ARIMA results
  best_fit$order[[n]]$ARIMA_p = ARIMA_p
  best_fit$order[[n]]$ARIMA_d = ARIMA_d
  best_fit$order[[n]]$ARIMA_q = ARIMA_q
  #Store the GARCH results
  best_fit$spec[[n]] = final.garch.spec
  best_fit$final_fit[[n]] = final.garch.fit
  best_fit$order[[n]]$GARCH_p = final.garchOrder[1]
  best_fit$order[[n]]$GARCH_q = final.garchOrder[2]
  #Store the AICs
  best_fit$ARIMA_AIC[n] <- df_arima_results$AIC[m]
  best_fit$GARCH_AIC[n] <- final.aic
}

#Save to RDS
saveRDS(best_fit, "data/best_fit.rds")

#Delete from memory
rm(arimaFit, df_arima_results, df_xts, final.garch.fit,
   final.garch.spec, garchFit, spec, ARIMA_d, ARIMA_p, 
   ARIMA_q, current.aic,current.symbol, final.aic, final.garchOrder,
   i, m, MAX_ARIMA_P, MAX_ARIMA_Q, MAX_GARCH_P, MAX_GARCH_Q, n, p, 
   q)
```
Load
```{r}
best_fit <- readRDS("data/best_fit.rds")
```

```{r}
#Construct the uGARCHfit and uGARCHspec objects
# best_fit$spec <- map(best_fit$order, function(order){
#   ARIMA_p = order$ARIMA_p
#   ARIMA_d = order$ARIMA_d
#   ARIMA_q = order$ARIMA_q
#   GARCH_p = order$GARCH_p
#   GARCH_q = order$GARCH_q
#   
#   result <- ugarchspec(
#     variance.model=list(model ="eGARCH",
#                         #submodel = "TGARCH",
#                         garchOrder=c(GARCH_p, GARCH_q)),
#     mean.model=list(armaOrder=c(ARIMA_p, 
#                                 ARIMA_q), 
#                     include.mean=T),
#     distribution.model="sged"
#   )
#   return(result)
# })
# 
# best_fit$final_fit <- map(best_fit$spec, )
```

Get the residuals and fitted values
```{r, warning = FALSE}
df_garch_results <- all_stock_train %>%
  bind_cols(
    map(best_fit$final_fit, residuals) %>%
    set_names(paste(ticker, ".resid", sep = "")) %>%
    as_tibble() 
  ) %>%
  bind_cols(
    map(best_fit$final_fit, residuals, standardize = TRUE) %>%
    set_names(paste(ticker, ".std_resid", sep = "")) %>%
    as_tibble()
  ) %>%
  bind_cols(
    map(best_fit$final_fit, sigma) %>%
    set_names(paste(ticker, ".sigma", sep = "")) %>%
    as_tibble()
  ) %>%
  bind_cols(
    map(best_fit$final_fit, fitted) %>%
    set_names(paste(ticker, ".fitted", sep = "")) %>%
    as_tibble()
  )

ggplot(df_garch_results %>%
         select(date, ends_with(".resid")) %>%
         pivot_longer(cols = -date,
                      names_to = "symbol",
                      values_to = "residual")) +
  geom_line(aes(x=date, y = residual, color = symbol)) +
  ggtitle("Non-standardised residuals from ARIMA-GARCH")

ggplot(df_garch_results %>%
         select(date, ends_with(".std_resid")) %>%
         pivot_longer(cols = -date,
                      names_to = "symbol",
                      values_to = "std_residual")) +
  geom_line(aes(x=date, y = std_residual, color = symbol)) +
  ggtitle("Standardised residuals from ARIMA-GARCH")
```

Extract the coefficients of the standardised residual distributions, 
and append it to the best_fit df
```{r, warning= FALSE}
library(fGarch)
best_fit <- best_fit %>%
  full_join(
    df_garch_results %>%
    select(ends_with(".std_resid")) %>%
    pivot_longer(cols = everything(),
                 names_to = "symbol",
                 values_to = "std_resid") %>%
    mutate(symbol = gsub(".std_resid","",symbol)) %>%
    group_by(symbol) %>%
    summarise(std_resid.mean = mean(std_resid),
              std_resid.sd = sd(std_resid)) %>%
    bind_cols(std_resid.shape = sapply(map(best_fit$final_fit, coef), 
                                       function(x){x["shape"]})) %>%
    bind_cols(std_resid.skew = sapply(map(best_fit$final_fit, coef), 
                            function(x){x["skew"]})),
    by = "symbol")
```
```{r}
df_fitted_pdf <- df_garch_results %>%
  select(ends_with(".std_resid")) %>%
  pivot_longer(cols = everything(),
               names_to = "symbol",
               values_to = "std_resid") %>%
  mutate(symbol = gsub(".std_resid","",symbol)) %>%
  left_join(best_fit %>% select(c(symbol,
                                  std_resid.mean:std_resid.skew)),
            by = "symbol") %>%
  mutate(norm_pdf = dnorm(std_resid, 
                          mean= std_resid.mean,
                          sd = std_resid.sd))
if(ERR_DIST == "sged"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsged(std_resid, 
                            mean= std_resid.mean,
                            sd = std_resid.sd,
                            nu = std_resid.shape,
                            xi = std_resid.skew))
} else if(ERR_DIST == "sstd"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsstd(std_resid, 
                            mean= std_resid.mean,
                            sd = std_resid.sd,
                            nu = std_resid.shape,
                            xi = std_resid.skew))
} else if(ERR_DIST == "std"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dstd(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           nu = std_resid.shape))
} else if(ERR_DIST == "ged"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dged(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           nu = std_resid.shape))
} else if(ERR_DIST == "snorm"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsnorm(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           xi = std_resid.skew))
} else if(ERR_DIST == "norm") {
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = norm_pdf)
}
  

ggplot(df_fitted_pdf) +
  geom_density(aes(x=std_resid, color = "Actual std resid")) +
  geom_line(aes(x=std_resid, y=norm_pdf, color = "Theoretical Normal"))+
  geom_line(aes(x=std_resid, y=std_err_pdf, color = paste("Theoretical", ERR_DIST)))+
  facet_wrap(~symbol)+
  ggtitle("Standardised Residual, theoretical distribution vs actual")
```
Using t-distribution for standardised residuals. seems that AMZN fits pretty well except for some end tail, and MSFT fits normal better for this case


```{r}
ggplot(df_fitted_pdf) +
  stat_ecdf(aes(x=std_resid, color = "actual ecdf")) +
  facet_wrap(~symbol)
```


```{r}
ggplot(df_fitted_pdf) +
  geom_qq(aes(sample=std_resid),
               distribution = fGarch::qstd,
               dparams = list(mean = df_fitted_pdf$std_resid.mean,
                              sd = df_fitted_pdf$std_resid.sd,
                              nu = df_fitted_pdf$std_resid.shape)) +
  facet_wrap(~symbol)
```

===========

```{r}
#Transform the standardised residuals into CDF of selected standardised error distribution

df_cdf_std_resid <- df_fitted_pdf %>%
  mutate(AMZN_CDF = pstd(AMZN,
                           mean = mean(AMZN),
                           sd = sd(AMZN),
                           nu = coef(best_fit$final_fit[[1]])["shape"],
                           xi = coef(best_fit$final_fit[[1]])["skew"])) %>%
  mutate(MSFT_CDF = pnorm(MSFT,
                           mean = mean(MSFT),
                           sd = sd(MSFT)))
ggplot(df_cdf_std_resid)+
  geom_histogram(aes(x=AMZN_CDF, fill="AMZN"))+
  ggtitle("Density of standardised residual CDF")
ggplot(df_cdf_std_resid)+
  geom_histogram(aes(x=MSFT_CDF, fill="MSFT"))+
  ggtitle("Density of standardised residual CDF")
```

Plot the two in a scatter plot
```{r}
ggplot(df_cdf_std_resid,
       aes(x = AMZN_CDF,
           y = MSFT_CDF)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Check the correlation between the two stocks and their CDF
```{r}
library(psych)
#NOTE all are residuals of the ARIMA-GARCH model
pairs.panels(df_cdf_std_resid %>% select(AMZN_CDF, MSFT_CDF))
pairs.panels(df_cdf_std_resid %>% select(AMZN, MSFT))
```

Fit a Copula to the stocks
Restrict to independent, gaussian and t copula
Note 16/11/2021 - Study other kinds of copula. When unrestricted, the function tries to fit a "survival BB8" copula. Not sure what that is.
```{r}
library(VineCopula)
u1 <- df_cdf_std_resid$AMZN_CDF
u2 <- df_cdf_std_resid$MSFT_CDF
selectedCopula <- BiCopSelect(u1 = u1, u2 = u2, familyset = c(0:2))
selectedCopula
```

Fit it using copula library, should give the same result as the above
```{r}
library(copula)
t.cop <- tCopula(dim=2)
fit <- fitCopula(t.cop,cbind(u1,u2),method='ml')
coef(fit)
```

Create n random samples from the copula, see if they look similar to the AMZN and MSFT data we had

```{r}
n = 100000
param1 = coef(fit)["rho.1"]
param2 = coef(fit)["df"]
set.seed(1)
uRandom <- rCopula(n, tCopula(c(param1), dim =2, df= param2))

#Construct a df, and plot
df_copula <- df_cdf_std_resid %>% 
  select(AMZN_CDF, MSFT_CDF) %>%
  mutate(label = "actual") %>%
  bind_rows(tibble(AMZN_CDF = uRandom[,1],
                   MSFT_CDF = uRandom[,2],
                   label = "random generation"))

ggplot(df_copula)+
  geom_point(aes(x=AMZN_CDF,
                 y=MSFT_CDF,
                 color = label)) +
  ggtitle("Randomly Generated t-Copula")

```

Use the randomly generated CDF returns from the Copula and compare it with the actual return
```{r}
mean = mean(df_std_resid$AMZN)
sd = sd(df_std_resid$AMZN)
nu = coef(best_fit$final_fit[[1]])["shape"]
xi = coef(best_fit$final_fit[[1]])["skew"]

df_copula <- df_copula %>%
  mutate(AMZN_RAND_RESID = qsged(AMZN_CDF,
                                 mean = mean,
                                 sd = sd,
                                 nu = nu,
                                 xi = xi))

mean = mean(df_std_resid$MSFT)
sd = sd(df_std_resid$MSFT)

df_copula <- df_copula %>%
  mutate(MSFT_RAND_RESID = qnorm(MSFT_CDF,
                                 mean = mean,
                                 sd = sd))

#Plus calcualte the copula (joint probability)
param1 = coef(fit)["rho.1"]
param2 = coef(fit)["df"]

joint_prob <- dCopula(array(c(df_copula$AMZN_CDF, df_copula$MSFT_CDF), 
                            dim = c(length(df_copula$AMZN_CDF), 2)), 
                      tCopula(c(param1), dim =2, df= param2))

df_copula <- df_copula %>%
  bind_cols(joint_prob = joint_prob)


ggplot(df_copula) +
  geom_density(aes(x=AMZN_RAND_RESID, color = label)) +
  ggtitle("AMZN actual vs randomly generated standardised residuals")

ggplot(df_copula) +
  geom_density(aes(x=MSFT_RAND_RESID, color = label)) +
  ggtitle("MSFT actual vs randomly generated standardised residuals")
```
Use the randomly generated standardised residuals to construct a 5% VaR of a portfolio of 50% AMZN and 50% MSFT.

Steps:
1. Using the randomly generated residuals, calculate the 1 step estimate, i.e.

$$ X_{t} = ARIMA + e_t$$
$$ e_t = \sigma_t * u_t$$
u_t is the randomly generated standardised residuals
$$ \sigma_t^2 = GARCH$$



```{r}
#Get the standardised residuals which were randomly generated before
df_VaR_std_resid <- df_copula %>% filter(label=="random generation") %>%
  select(AMZN_RAND_RESID, MSFT_RAND_RESID) %>%
  rename(AMZN_std_resid = AMZN_RAND_RESID) %>%
  rename(MSFT_std_resid = MSFT_RAND_RESID)

#Calculate the residuals = sigma * standardised residuals
df_VaR <- tibble(date = index(sigma(best_fit$final_fit[[1]])),
                 AMZN_sigma = sigma(best_fit$final_fit[[1]])) %>%
  full_join(tibble(date = index(sigma(best_fit$final_fit[[2]])),
                   MSFT_sigma = sigma(best_fit$final_fit[[2]])),
            by = "date")
df_VaR <- df_VaR %>%
  bind_cols("AMZN_resid" = coredata(df_VaR$AMZN_sigma) %*% t(df_VaR_std_resid$AMZN_std_resid))%>%
  bind_cols("MSFT_resid" = coredata(df_VaR$MSFT_sigma) %*% t(df_VaR_std_resid$MSFT_std_resid))

#Plot one of the realisation
plot(density(df_VaR$AMZN_resid[1,]))

#Calculate the 5% VaR
temp <- matrix(0, nrow = nrow(df_VaR), ncol = 2)
for (i in 1:nrow(df_VaR)){
  temp[i,1] <- quantile(df_VaR$AMZN_resid[i,], prob = 0.05)
  temp[i,2] <- quantile(df_VaR$MSFT_resid[i,], prob = 0.05)
}

df_VaR <- df_VaR %>%
  bind_cols(AMZN_VaR = temp[,1]) %>%
  bind_cols(MSFT_VaR = temp[,2])

#Combine the fitted value with the VaR
df_VaR <- df_VaR %>%
  bind_cols(AMZN_fitted = fitted(best_fit$final_fit[[1]])) %>%
  bind_cols(MSFT_fitted = fitted(best_fit$final_fit[[2]])) %>%
  mutate(AMZN_VaR = AMZN_fitted + AMZN_VaR) %>%
  mutate(MSFT_VaR = MSFT_fitted + MSFT_VaR) 

#Combine with the actual return data
df_VaR <- df_VaR %>%
  bind_cols(all_stock_train %>% 
              filter(symbol == "AMZN") %>%
              select(lret) %>%
              rename(AMZN_actual = lret)) %>%
  bind_cols(all_stock_train %>% 
              filter(symbol == "MSFT") %>%
              select(lret) %>%
              rename(MSFT_actual = lret))

#Plot each stock with its actual and VaR
ggplot(df_VaR)+
  geom_line(aes(x= date, y=AMZN_actual, color= "actual")) +
  geom_line(aes(x= date, y=AMZN_fitted, color= "fitted")) +
  geom_line(aes(x= date, y=AMZN_VaR, color= "5% VaR")) +
  ggtitle("AMZN Return and 5% VaR")

ggplot(df_VaR)+
  geom_line(aes(x= date, y=MSFT_actual, color= "actual")) +
  geom_line(aes(x= date, y=MSFT_fitted, color= "fitted")) +
  geom_line(aes(x= date, y=MSFT_VaR, color= "5% VaR")) +
  ggtitle("MSFT Return and 5% VaR")

#Calculate number of exceedance of 5% VaR

df_VaR %>% 
  mutate(AMZN_exceed = AMZN_actual<AMZN_VaR) %>%
  mutate(MSFT_exceed = MSFT_actual<MSFT_VaR) %>%
  select(AMZN_exceed, MSFT_exceed) %>%
  pivot_longer(cols = c(AMZN_exceed, MSFT_exceed),
               names_to = "symbol",
               values_to = "exceed") %>%
  group_by(symbol) %>%
  summarise(exceed_num = sum(exceed),
            exceed_prop = sum(exceed)/nrow(df_VaR),
            expected = 0.05*nrow(df_VaR))


```

Explore the CDF of the actual and fitted return
Using the simulated return data
Note the fitted return will always be close to 50% quantile, as by definition they are the mean

```{r}
df_return_cdf <- df_VaR %>% 
  select(date, 
         AMZN_resid, MSFT_resid, 
         AMZN_fitted, MSFT_fitted, 
         AMZN_actual, MSFT_actual)

#Calculate the simulated portfolio returns
temp_sim_AMZN <- matrix(0, 
                    nrow = nrow(df_return_cdf$AMZN_resid), 
                    ncol = ncol(df_return_cdf$AMZN_resid))
temp_sim_MSFT <- matrix(0, 
                    nrow = nrow(df_return_cdf$MSFT_resid), 
                    ncol = ncol(df_return_cdf$MSFT_resid))
#Calculate the CDF of the actual return
temp_actual_AMZN <- matrix(0, 
                    nrow = nrow(df_return_cdf$AMZN_resid), 
                    ncol = 1)
temp_actual_MSFT <- matrix(0, 
                    nrow = nrow(df_return_cdf$MSFT_resid), 
                    ncol = 1)
#Calculate the CDF of the fitted return
temp_fitted_AMZN <- temp_actual_AMZN
temp_fitted_MSFT <- temp_actual_MSFT

#Function to return empirical quantile (CDF) given data and the number
equantile <- function(data, value){
    tmp_a <- ecdf(data)
    return(tmp_a(value))
}

#Note the performance of the loop is very poor. Need to look into the data structure and find more efficient ways of doing this

for (i in 1:nrow(df_return_cdf)){
  #Calculate the simulated portfolio returns
  temp_sim_AMZN[i,] <- df_return_cdf$AMZN_resid[i,] + rep(df_return_cdf$AMZN_fitted[i], times = ncol(temp_sim_AMZN))
  temp_sim_MSFT[i,] <- df_return_cdf$MSFT_resid[i,] + rep(df_return_cdf$MSFT_fitted[i], times = ncol(temp_sim_AMZN))
  
  #Calculate the CDF of the actual return
  temp_actual_AMZN[i] <- equantile(temp_sim_AMZN[i,],
                                   df_return_cdf$AMZN_actual[i])
  temp_actual_MSFT[i] <- equantile(temp_sim_MSFT[i,],
                                df_return_cdf$MSFT_actual[i])
  
  #Calculate the CDF of the fitted return
  temp_fitted_AMZN[i] <- equantile(temp_sim_AMZN[i,],
                                df_return_cdf$AMZN_fitted[i])
  temp_fitted_MSFT[i] <- equantile(temp_sim_MSFT[i,],
                                df_return_cdf$MSFT_fitted[i])
}

df_return_cdf <- df_return_cdf %>%
  bind_cols("AMZN_simulated_return" = temp_sim_AMZN) %>%
  bind_cols("MSFT_simulated_return" = temp_sim_MSFT) %>%
  bind_cols("AMZN_actual_quantile" = temp_actual_AMZN) %>%
  bind_cols("MSFT_actual_quantile" = temp_actual_MSFT) %>%
  bind_cols("AMZN_fitted_quantile" = temp_fitted_AMZN) %>%
  bind_cols("MSFT_fitted_quantile" = temp_fitted_MSFT)

rm(temp_sim_AMZN, temp_sim_MSFT, 
   temp_actual_AMZN, temp_actual_MSFT,
   temp_fitted_AMZN, temp_fitted_MSFT)
```

Plot the CDF
```{r}
#Plot the results
plot_return_cdf <- ggplot(df_return_cdf) +
  geom_line(aes(x=date,
                 y=AMZN_actual_quantile,
                 color = "AMZN"))+
  geom_line(aes(x=date,
                 y=MSFT_actual_quantile,
                 color = "MSFT"))+
  geom_line(aes(x=date,
                 y=AMZN_fitted_quantile,
                 color = "AMZN fitted"))+
  geom_line(aes(x=date,
                 y=MSFT_fitted_quantile,
                 color = "MSFT fitted")) +
  geom_hline(aes(color = "5% VaR"),yintercept = 0.05)
  ggtitle("AMZN, MSFT actual and fitted return quantile based on empirical CDF of 100,000 randomly generated date from ARIMA-eGARCH-tCopula model")

ggplot(df_return_cdf)+
  stat_ecdf(aes(x= AMZN_actual_quantile,
                color = "AMZN"), 
            geom="line") +
  stat_ecdf(aes(x= MSFT_actual_quantile,
                color = "MSFT"), 
            geom="line") +
  geom_abline(aes(color = "Theoretical"),slope = 1, intercept = 0) +
  ggtitle("CDF distribution of AMZN, MSFT. 45 degree line indicates theoretical value")
  
library(plotly)
ggplotly(plot_return_cdf)
```
