---
title: "SPYTrade v1.1"
author: "Akbar Rizqiansyah"
date: "06/11/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
EVAL_GARCH_OPTION = FALSE
```

```{r}
library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)
library(xts)
library(tidyverse)
library(tidyquant)
```

```{r, warning = FALSE, echo = FALSE}
#Download data
ticker = c("AMZN",
          "MSFT")
all_stock <- tq_get(ticker,
              from = "2020-01-01",
              to = "2021-11-16",
              get = "stock.prices") %>%
  select(symbol, date, close) %>%
  mutate(lret = c(0, diff(log(close))))

#Turn all first days returns to 0
first_day <- all_stock %>%
  group_by(symbol) %>%
  summarise(date = min(date)) %>%
  left_join(all_stock, by = c("symbol" = "symbol", "date" = "date")) %>%
  mutate(lret = 0)

all_stock <- all_stock %>% 
  anti_join(first_day, by = c("symbol" = "symbol", "date" = "date")) %>%
  bind_rows(first_day) %>%
  arrange(date) 

#Remove N_VERIFICATION amount of observations for verification later
N_VERIFICATION = 14
all_stock_train <- all_stock %>% 
  filter(date < max(date) - days(N_VERIFICATION))
```


```{r}
#Find best fit ARIMA and GARCH (Asymmetric) specification for all stocks
best_fit <- tibble(symbol = ticker,
               ARIMA_AIC = Inf,
               GARCH_AIC = Inf,
               ARIMA_p = 1,
               ARIMA_d = 0,
               ARIMA_q = 1,
               GARCH_p = 1,
               GARCH_q = 1,
               spec = list(0),
               final_fit = list(0)) %>%
  nest(order = c(ARIMA_p, ARIMA_d, ARIMA_q, GARCH_p, GARCH_q))
```


# Find best ARIMA-GARCH model based on AIC
Note 16/11/2021 - 
Sometimes ugarchfit() fails to converge (example is AAPL data) for the best ARIMA lags, but converges for lower ARIMA lags. Maybe need to temporarily store the AIC of all ARIMA model, and walk backward the ARIMA model from best to worse AIC if GARCH fails to converge


```{r, eval = EVAL_GARCH_OPTION}
#Settings
MAX_ARIMA_P = 5
MAX_ARIMA_Q = 5
MAX_GARCH_P = 5
MAX_GARCH_Q = 5

for (i in c(1:length(ticker))) {
  #Temporary variables
  current.symbol <- ticker[i]
  df <- all_stock_train %>% 
    filter(symbol == current.symbol)
  df <- df$lret
  final.aic <- best_fit$ARIMA_AIC[i]
  final.order = c(0, 0, 0)
  
  for (p in 0:MAX_ARIMA_P) for (q in 0:MAX_ARIMA_Q) {
    if ( p == 0 && q == 0) {
      next
    }
    
    arimaFit = tryCatch( arima(df, order=c(p, 0, q)),
                         error=function( err ) {
                           message(err)
                           return(FALSE)
                         },
                         warning=function( err ) {
                           # message(err)
                           return(FALSE)
                         } )
    
    if( !is.logical( arimaFit ) ) {
      current.aic <- AIC(arimaFit)
      if (current.aic < final.aic) {
        final.aic <- current.aic
        final.order <- c(p, 0, q)
        # final.arima <- arima(df, order=final.order)
        final.arima <- arimaFit
      }
    } else {
      next
    }
  }

  # test for the case we have not achieved a solution  
  if (final.order[1]==0 && final.order[3]==0) {
    final.order[1] = 1
    final.order[3] = 1
  }
  #Store the ARIMA results
  best_fit$order[[i]]$ARIMA_p = final.order[1]
  best_fit$order[[i]]$ARIMA_d = final.order[2]
  best_fit$order[[i]]$ARIMA_q = final.order[3]
  
  # Specify and fit the GARCH model
  #Temporary variables
  final.aic <- best_fit$GARCH_AIC[i]
  final.garchOrder <- c(0,0)
  for (p in 1:MAX_GARCH_P) for (q in 1:MAX_GARCH_Q) {
    print(paste("Stock =", current.symbol, "p =", p, "q =", q))
    spec = ugarchspec(
      variance.model=list(model ="eGARCH",
                          #submodel = "TGARCH",
                          garchOrder=c(p,q)),
      mean.model=list(armaOrder=c(final.order[1], 
                                  final.order[3]), 
                                  include.mean=T),
      distribution.model="sged"
    )
    garchFit = tryCatch(
      ugarchfit(
        spec, df, solver = 'hybrid'
      ), 
      error=function( err ) {
                           message(err)
                           return(FALSE)
                         },
      warning=function( err ) {
                           #message(err)
                           return(FALSE)
                         } )
    
    if( !is.logical( garchFit ) ) {
      current.aic <- infocriteria(garchFit)[1]
      if (current.aic < final.aic) {
        final.aic <- current.aic
        final.garchOrder <- c(p, q)
        final.garch.spec <- spec
        final.garch.fit <- garchFit
      }
    } else {
      next
    }
  }
  #Store the GARCH results
  best_fit$spec[[i]] = final.garch.spec
  best_fit$final_fit[[i]] = final.garch.fit
  best_fit$order[[i]]$GARCH_p = final.garchOrder[1]
  best_fit$order[[i]]$GARCH_q = final.garchOrder[2]
}
saveRDS(best_fit, "data/best_fit.rds")
```
Load
```{r}
best_fit <- readRDS("data/best_fit.rds")
```

```{r}
#Construct the uGARCHfit and uGARCHspec objects
# best_fit$spec <- map(best_fit$order, function(order){
#   ARIMA_p = order$ARIMA_p
#   ARIMA_d = order$ARIMA_d
#   ARIMA_q = order$ARIMA_q
#   GARCH_p = order$GARCH_p
#   GARCH_q = order$GARCH_q
#   
#   result <- ugarchspec(
#     variance.model=list(model ="eGARCH",
#                         #submodel = "TGARCH",
#                         garchOrder=c(GARCH_p, GARCH_q)),
#     mean.model=list(armaOrder=c(ARIMA_p, 
#                                 ARIMA_q), 
#                     include.mean=T),
#     distribution.model="sged"
#   )
#   return(result)
# })
# 
# best_fit$final_fit <- map(best_fit$spec, )
```

```{r}
df_resid <- tibble(date = index(residuals(best_fit$final_fit[[1]])),
                       AMZN = coredata(residuals(best_fit$final_fit[[1]]))) %>%
  full_join(tibble(date = index(residuals(best_fit$final_fit[[2]])),
                   MSFT = coredata(residuals(best_fit$final_fit[[2]]))),
            by = "date")

ggplot(df_resid) +
  geom_line(aes(x = date,
                y = AMZN,
                color = "AMZN")) +
  geom_line(aes(x = date,
                y = MSFT,
                color = "MSFT")) +
  ggtitle("Residuals (Not Standardised)")
```

```{r}
df_std_resid <- tibble(date = index(residuals(best_fit$final_fit[[1]], 
                                              standardize = T)),
                       AMZN = coredata(residuals(best_fit$final_fit[[1]], 
                                              standardize = T))) %>%
  full_join(tibble(date = index(residuals(best_fit$final_fit[[2]], 
                                              standardize = T)),
                   MSFT = coredata(residuals(best_fit$final_fit[[2]], 
                                              standardize = T))),
            by = "date")

ggplot(df_std_resid) +
  geom_line(aes(x = date,
                y = AMZN,
                color = "AMZN")) +
  geom_line(aes(x = date,
                y = MSFT,
                color = "MSFT")) +
  ggtitle("Standardised Residuals")

ggplot(df_std_resid,
       aes(x = AMZN,
           y = MSFT)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Scatter plot of standardised residuals. Note the non normal behaviour of the two") +
  xlab("AMZN") +
  ylab("MSFT")
```

```{r}
#Check the distribution of AMZN and MSFT
#against normal and SGED distributions
library(fGarch)

df_fitted_std_resid <- df_std_resid %>%
  mutate(norm.AMZN = dnorm(AMZN, 
                           mean = mean(AMZN),
                           sd = sd(AMZN))) %>%
  mutate(sged.AMZN = dsged(AMZN,
                           mean = mean(AMZN),
                           sd = sd(AMZN),
                           nu = coef(best_fit$final_fit[[1]])["shape"],
                           xi = coef(best_fit$final_fit[[1]])["skew"])) %>%
  mutate(norm.MSFT = dnorm(MSFT, 
                           mean = mean(MSFT),
                           sd = sd(MSFT))) %>%
  mutate(sged.MSFT = dsged(MSFT,
                           mean = mean(MSFT),
                           sd = sd(MSFT),
                           nu = coef(best_fit$final_fit[[2]])["shape"],
                           xi = coef(best_fit$final_fit[[2]])["skew"]))
ggplot(df_fitted_std_resid) +
  geom_density(aes(x=AMZN)) +
  geom_point(aes(x=AMZN, y=norm.AMZN, color="Normal")) +
  geom_point(aes(x=AMZN, y=sged.AMZN, color="SGED"))+
  ggtitle("AMZN standardised residuals density")

ggplot(df_fitted_std_resid) +
  geom_density(aes(x=MSFT)) +
  geom_point(aes(x=MSFT, y=norm.MSFT, color="Normal")) +
  geom_point(aes(x=MSFT, y=sged.MSFT, color="SGED"))+
  ggtitle("MSFT standardised residuals density")

```
Seems like AMZN fits SGED better while MSFT fits normal better. Check if we map to the CDF, we get somewhat close to a uniform distribution

```{r}
#Transform the standardised residuals into CDF of Skewed Generalised Error Distribution (SGED) and/or normal

df_cdf_std_resid <- df_std_resid %>%
  mutate(AMZN_CDF = psged(AMZN,
                           mean = mean(AMZN),
                           sd = sd(AMZN),
                           nu = coef(best_fit$final_fit[[1]])["shape"],
                           xi = coef(best_fit$final_fit[[1]])["skew"])) %>%
  mutate(MSFT_CDF = pnorm(MSFT,
                           mean = mean(MSFT),
                           sd = sd(MSFT)))
ggplot(df_cdf_std_resid)+
  geom_histogram(aes(x=AMZN_CDF, fill="AMZN"))+
  ggtitle("Density of standardised residual CDF")
ggplot(df_cdf_std_resid)+
  geom_histogram(aes(x=MSFT_CDF, fill="MSFT"))+
  ggtitle("Density of standardised residual CDF")
```

Plot the two in a scatter plot
```{r}
ggplot(df_cdf_std_resid,
       aes(x = AMZN_CDF,
           y = MSFT_CDF)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Check the correlation between the two stocks and their CDF
```{r}
library(psych)
#NOTE all are residuals of the ARIMA-GARCH model
pairs.panels(df_cdf_std_resid %>% select(AMZN_CDF, MSFT_CDF))
pairs.panels(df_cdf_std_resid %>% select(AMZN, MSFT))
```

Fit a Copula to the stocks
Restrict to independent, gaussian and t copula
Note 16/11/2021 - Study other kinds of copula. When unrestricted, the function tries to fit a "survival BB8" copula. Not sure what that is.
```{r}
library(VineCopula)
u1 <- df_cdf_std_resid$AMZN_CDF
u2 <- df_cdf_std_resid$MSFT_CDF
selectedCopula <- BiCopSelect(u1 = u1, u2 = u2, familyset = c(0:2))
selectedCopula
```

Fit it using copula library, should give the same result as the above
```{r}
library(copula)
t.cop <- tCopula(dim=2)
fit <- fitCopula(t.cop,cbind(u1,u2),method='ml')
coef(fit)
```

Create n random samples from the copula, see if they look similar to the AMZN and MSFT data we had

```{r}
n = 100000
param1 = coef(fit)["rho.1"]
param2 = coef(fit)["df"]
set.seed(1)
uRandom <- rCopula(n, tCopula(c(param1), dim =2, df= param2))

#Construct a df, and plot
df_copula <- df_cdf_std_resid %>% 
  select(AMZN_CDF, MSFT_CDF) %>%
  mutate(label = "actual") %>%
  bind_rows(tibble(AMZN_CDF = uRandom[,1],
                   MSFT_CDF = uRandom[,2],
                   label = "random generation"))

ggplot(df_copula)+
  geom_point(aes(x=AMZN_CDF,
                 y=MSFT_CDF,
                 color = label)) +
  ggtitle("Randomly Generated t-Copula")

```

Use the randomly generated CDF returns from the Copula and compare it with the actual return
```{r}
mean = mean(df_std_resid$AMZN)
sd = sd(df_std_resid$AMZN)
nu = coef(best_fit$final_fit[[1]])["shape"]
xi = coef(best_fit$final_fit[[1]])["skew"]

df_copula <- df_copula %>%
  mutate(AMZN_RAND_RESID = qsged(AMZN_CDF,
                                 mean = mean,
                                 sd = sd,
                                 nu = nu,
                                 xi = xi))

mean = mean(df_std_resid$MSFT)
sd = sd(df_std_resid$MSFT)

df_copula <- df_copula %>%
  mutate(MSFT_RAND_RESID = qnorm(MSFT_CDF,
                                 mean = mean,
                                 sd = sd))

#Plus calcualte the copula (joint probability)
param1 = coef(fit)["rho.1"]
param2 = coef(fit)["df"]

joint_prob <- dCopula(array(c(df_copula$AMZN_CDF, df_copula$MSFT_CDF), 
                            dim = c(length(df_copula$AMZN_CDF), 2)), 
                      tCopula(c(param1), dim =2, df= param2))

df_copula <- df_copula %>%
  bind_cols(joint_prob = joint_prob)


ggplot(df_copula) +
  geom_density(aes(x=AMZN_RAND_RESID, color = label)) +
  ggtitle("AMZN actual vs randomly generated standardised residuals")

ggplot(df_copula) +
  geom_density(aes(x=MSFT_RAND_RESID, color = label)) +
  ggtitle("MSFT actual vs randomly generated standardised residuals")
```
Use the randomly generated standardised residuals to construct a 5% VaR of a portfolio of 50% AMZN and 50% MSFT.

Steps:
1. Using the randomly generated residuals, calculate the 1 step estimate, i.e.

$$ X_{t} = ARIMA + e_t$$
$$ e_t = \sigma_t * u_t$$
u_t is the randomly generated standardised residuals
$$ \sigma_t^2 = GARCH$$



```{r}
#Get the standardised residuals which were randomly generated before
df_VaR_std_resid <- df_copula %>% filter(label=="random generation") %>%
  select(AMZN_RAND_RESID, MSFT_RAND_RESID) %>%
  rename(AMZN_std_resid = AMZN_RAND_RESID) %>%
  rename(MSFT_std_resid = MSFT_RAND_RESID)

#Calculate the residuals = sigma * standardised residuals
df_VaR <- tibble(date = index(sigma(best_fit$final_fit[[1]])),
                 AMZN_sigma = sigma(best_fit$final_fit[[1]])) %>%
  full_join(tibble(date = index(sigma(best_fit$final_fit[[2]])),
                   MSFT_sigma = sigma(best_fit$final_fit[[2]])),
            by = "date")
df_VaR <- df_VaR %>%
  bind_cols("AMZN_resid" = coredata(df_VaR$AMZN_sigma) %*% t(df_VaR_std_resid$AMZN_std_resid))%>%
  bind_cols("MSFT_resid" = coredata(df_VaR$MSFT_sigma) %*% t(df_VaR_std_resid$MSFT_std_resid))

#Plot one of the realisation
plot(density(df_VaR$AMZN_resid[1,]))

#Calculate the 5% VaR
temp <- matrix(0, nrow = nrow(df_VaR), ncol = 2)
for (i in 1:nrow(df_VaR)){
  temp[i,1] <- quantile(df_VaR$AMZN_resid[i,], prob = 0.05)
  temp[i,2] <- quantile(df_VaR$MSFT_resid[i,], prob = 0.05)
}

df_VaR <- df_VaR %>%
  bind_cols(AMZN_VaR = temp[,1]) %>%
  bind_cols(MSFT_VaR = temp[,2])

#Combine the fitted value with the VaR
df_VaR <- df_VaR %>%
  bind_cols(AMZN_fitted = fitted(best_fit$final_fit[[1]])) %>%
  bind_cols(MSFT_fitted = fitted(best_fit$final_fit[[2]])) %>%
  mutate(AMZN_VaR = AMZN_fitted + AMZN_VaR) %>%
  mutate(MSFT_VaR = MSFT_fitted + MSFT_VaR) 

#Combine with the actual return data
df_VaR <- df_VaR %>%
  bind_cols(all_stock_train %>% 
              filter(symbol == "AMZN") %>%
              select(lret) %>%
              rename(AMZN_actual = lret)) %>%
  bind_cols(all_stock_train %>% 
              filter(symbol == "MSFT") %>%
              select(lret) %>%
              rename(MSFT_actual = lret))

#Plot each stock with its actual and VaR
ggplot(df_VaR)+
  geom_line(aes(x= date, y=AMZN_actual, color= "actual")) +
  geom_line(aes(x= date, y=AMZN_fitted, color= "fitted")) +
  geom_line(aes(x= date, y=AMZN_VaR, color= "5% VaR")) +
  ggtitle("AMZN Return and 5% VaR")

ggplot(df_VaR)+
  geom_line(aes(x= date, y=MSFT_actual, color= "actual")) +
  geom_line(aes(x= date, y=MSFT_fitted, color= "fitted")) +
  geom_line(aes(x= date, y=MSFT_VaR, color= "5% VaR")) +
  ggtitle("MSFT Return and 5% VaR")

#Calculate number of exceedance of 5% VaR

df_VaR %>% 
  mutate(AMZN_exceed = AMZN_actual<AMZN_VaR) %>%
  mutate(MSFT_exceed = MSFT_actual<MSFT_VaR) %>%
  select(AMZN_exceed, MSFT_exceed) %>%
  pivot_longer(cols = c(AMZN_exceed, MSFT_exceed),
               names_to = "symbol",
               values_to = "exceed") %>%
  group_by(symbol) %>%
  summarise(exceed_num = sum(exceed),
            exceed_prop = sum(exceed)/nrow(df_VaR),
            expected = 0.05*nrow(df_VaR))


```

Simple 2 portfolio analysis. Calculate VaR for the portfolio.

```{r}
fn_simple_portfolio <- function(weight1){
  print(paste("calculating simple portfolio weight = ", weight1))
  weight2 <- 1-weight1
  #Calculate the portfolio actual and fitted return
  df_portfolio <- df_VaR %>% 
    select(date, 
           AMZN_resid, MSFT_resid, 
           AMZN_fitted, MSFT_fitted, 
           AMZN_actual, MSFT_actual) %>%
    mutate(portfolio_actual = AMZN_actual*weight1 + MSFT_actual*weight2) %>%
    mutate(portfolio_fitted = AMZN_fitted*weight1 + MSFT_fitted*weight2)
  
  #Calculate the simulated portfolio returns
  temp_AMZN <- matrix(0, 
                      nrow = nrow(df_portfolio$AMZN_resid), 
                      ncol = ncol(df_portfolio$AMZN_resid))
  temp_MSFT <- matrix(0, 
                      nrow = nrow(df_portfolio$MSFT_resid), 
                      ncol = ncol(df_portfolio$MSFT_resid))
  temp_portfolio <- matrix(0, 
                      nrow = nrow(df_portfolio$MSFT_resid), 
                      ncol = ncol(df_portfolio$MSFT_resid))
  
  for (i in 1:nrow(df_VaR)){
    temp_AMZN[i,] <- df_portfolio$AMZN_resid[i,] + rep(df_portfolio$AMZN_fitted[i], times = ncol(temp_AMZN))
    temp_MSFT[i,] <- df_portfolio$MSFT_resid[i,] + rep(df_portfolio$MSFT_fitted[i], times = ncol(temp_AMZN))
    temp_portfolio[i,] <- temp_AMZN[i,]*weight1 + temp_MSFT[i,]*weight2
  }
  
  df_portfolio <- df_portfolio %>%
    bind_cols("portfolio_simulated" = temp_portfolio) %>%
    select(-c(AMZN_resid, MSFT_resid,
              AMZN_fitted, MSFT_fitted,
              AMZN_actual, MSFT_actual))
  
  #Calculated the portfolio VaR from the simulated returns
  temp <- matrix(0, nrow = nrow(df_VaR), ncol = 1)
  for (i in 1:nrow(df_VaR)){
    temp[i,1] <- quantile(df_portfolio$portfolio_simulated[i,], prob = 0.05)
  }
  
  df_portfolio <- df_portfolio %>%
    bind_cols("portfolio_VaR" = temp)
  return(df_portfolio)
}
  
fn_simple_portfolio_summary <- function(df_portfolio){
  #Exceedance and Expected shortfall (ES)
  result <- df_portfolio %>% 
    mutate(portfolio_exceed = portfolio_actual<portfolio_VaR) %>%
    mutate(portfolio_shortfall = portfolio_actual*portfolio_exceed) %>%
    summarise(exceed_num = sum(portfolio_exceed),
              exceed_prop = sum(portfolio_exceed)/nrow(df_portfolio),
              expected_exceedance = 0.05*nrow(df_portfolio),
              expected_shortfall = sum(portfolio_shortfall)/sum(portfolio_exceed))
  
  return(result)
}
```


```{r}
weight_vector <- seq(from = 0, to = 1, by = 0.1)
portfolio_summary <- map_df(weight_vector,
     function(.x){fn_simple_portfolio_summary(fn_simple_portfolio(.x))})
portfolio_summary <- portfolio_summary %>%
  bind_cols(weight1 = weight_vector)
portfolio_summary
```

```{r}
portfolio_VaR <- map_df(weight_vector,
     function(.x){fn_simple_portfolio(.x)})
```

```{r}
#Plot all the VaRs
a<-portfolio_VaR$portfolio_VaR
b<-matrix(a, nrow = length(a)/length(weight_vector), ncol = length(weight_vector))

df_plot_VaR <- df_VaR %>%
  select(date) %>%
  cbind(b) %>%
  pivot_longer(cols = -c(date),
               names_to = "label",
               values_to = "VaR") %>%
  mutate(weight1 = weight_vector[as.numeric(label)]) %>%
  select(-label)

a<-portfolio_VaR$portfolio_actual
b<-matrix(a, nrow = length(a)/length(weight_vector), ncol = length(weight_vector))
df_plot_actual <-  df_VaR %>%
  select(date) %>%
  cbind(b) %>%
  pivot_longer(cols = -c(date),
               names_to = "label",
               values_to = "actual") %>%
  mutate(weight1 = weight_vector[as.numeric(label)]) %>%
  select(-label)

df_plot <- df_plot_VaR %>%
  full_join(df_plot_actual,
            by = c("date", "weight1"))

ggplot(df_plot) +
  geom_line(aes(x=date,
                y=VaR,
                color = weight1))+
  geom_line(aes(x=date,
                y=actual,
                color = weight1))+
  ggtitle("Portfolio Actual Return and 5% VaR with various weight on AMZN")


var_ggplot <- ggplot(df_plot) +
  geom_line(aes(x=date,
                y=VaR,
                color = weight1))+
  ggtitle("5% VaR with various weight on AMZN")
  
actual_ggplot <- ggplot(df_plot) +
  geom_line(aes(x=date,
                y=actual,
                color = weight1))+
  ggtitle("Portfolio Actual Return with various weight on AMZN")


library(plotly)
ggplotly(var_ggplot)
ggplotly(actual_ggplot)
```



To do: Monte carlo VaR calculation:

VaR calculation based on this paper: https://www.sciencedirect.com/science/article/pii/S0167668709001267
Eqn. 24 to 27

$$ P(X_{p,t} \le VaR_t(\alpha))= \int_{-\infty}^{\infty} \int_{\infty}^{\frac{VaR_t(\alpha)}{2}-x_{2,t}} c(F(x_{1,t}), F(x_{2,t})|\Omega_{t-1})*f(x_{1,t}|\Omega{t-1})*f(x_{2,t}|\Omega{t-1}) dx_{1,t} dx_{2,t} = \alpha $$
Where
$$ X_{p,t} = wX_{1,t}+(1-w)X_{2,t}$$


Use Monte Carlo Integral to integrate over the VaR

```{r}


```




