---
title: "SPYTrade v1.1"
author: "Akbar Rizqiansyah"
date: "06/11/2021"
output: html_document
---

Objective:
Do proper out of sample forecasting (5 days), see how the model performs along the 5 days.
Also make the whole dataframe tidier, make it so it can handle more than 2 assets.
Actively delete unused objects and variables to save on memory.
Extension: look into multi path forecasting + data assimilation to combine the different estimates.

Difference to v2.5.2:
No LSTM estimates at the end

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
EVAL_GARCH_OPTION = FALSE
```

```{r}
library(quantmod)
library(lattice)
library(timeSeries)
library(rugarch)
library(xts)
library(tidyverse)
library(tidyquant)
library(visdat)
```

# 1.0 Data tidying
Download the data
```{r, warning = FALSE, echo = FALSE}
#Download data
ticker = c("AAPL",
           "AMZN",
           "MSFT",
           "NKE",
           "WMT",
           "WST",
           "MA",
           "LMT",
           "RTX",
           "REGN")
all_stock <- tq_get(ticker,
              from = "2011-11-01",
              to = "2021-11-01",
              get = "stock.prices") %>%
  select(symbol, date, close) %>%
  mutate(lret = c(0, diff(log(close))))

#Turn all first days returns to 0
first_day <- all_stock %>%
  group_by(symbol) %>%
  summarise(date = min(date)) %>%
  left_join(all_stock, by = c("symbol" = "symbol", "date" = "date")) %>%
  mutate(lret = 0)

all_stock <- all_stock %>% 
  anti_join(first_day, by = c("symbol" = "symbol", "date" = "date")) %>%
  bind_rows(first_day) %>%
  arrange(date)

#Delete objects
rm(first_day)
```

Split the data into training and verification data
2/3 training, 1/3 training
```{r}
#Split the data into its individual symbols
all_stock_lret <- pivot_wider(all_stock,
                              id_cols = date,
                              names_from = symbol,
                              values_from = lret,
                              names_glue = "{symbol}.lret")
all_stock_close <- pivot_wider(all_stock,
                               id_cols = date,
                               names_from = symbol,
                               values_from = close,
                               names_glue = "{symbol}.close")

all_stock <- all_stock_lret %>% 
  full_join(all_stock_close, by ="date")

#Remove 1/3 amount of observations for verification later
N_TRAIN = ceiling(nrow(all_stock_lret)*2/3)
N_VERIFICATION = nrow(all_stock_lret) - N_TRAIN

all_stock_train <- all_stock %>%
  head(N_TRAIN)

all_stock_verification <- all_stock %>%
  tail(N_VERIFICATION)

#Delete objects
rm(all_stock_lret, all_stock_close)
```

Check for any missing data
```{r}
vis_miss(all_stock %>% select(ends_with(".lret")))
vis_miss(all_stock %>% select(ends_with(".close")))
```
See correlation
See both Pearson's and Spearman's (Assuming no normal dependencies)
```{r}
library(ggcorrplot)
ggcorrplot(cor(all_stock%>%select(ends_with(".lret")), method = "pearson"), lab=TRUE)
ggcorrplot(cor(all_stock%>%select(ends_with(".lret")), method = "spearman"), lab=TRUE)
```
Let's stick with AMZN and MSFT first, then generalise if possible
```{r}
select_ticker = c("MSFT")

all_stock <- all_stock %>%
  select(date, starts_with(select_ticker))
all_stock_train <- all_stock_train %>%
  select(date, starts_with(select_ticker))
all_stock_verification <- all_stock_verification %>%
  select(date, starts_with(select_ticker))

ticker = select_ticker
```

# 2.0 Fit into ARIMA-eGARCH model
```{r}
#Find best fit ARIMA and GARCH (Asymmetric) specification for all stocks
best_fit <- tibble(symbol = ticker,
               ARIMA_AIC = Inf,
               GARCH_AIC = Inf,
               ARIMA_p = 1,
               ARIMA_d = 0,
               ARIMA_q = 1,
               GARCH_p = 1,
               GARCH_q = 1,
               spec = list(0),
               final_fit = list(0)) %>%
  nest(order = c(ARIMA_p, ARIMA_d, ARIMA_q, GARCH_p, GARCH_q))
```


# Find best ARIMA-GARCH model based on AIC
Note 16/11/2021 - 
Sometimes ugarchfit() fails to converge (example is AAPL data) for the best ARIMA lags, but converges for lower ARIMA lags. Maybe need to temporarily store the AIC of all ARIMA model, and walk backward the ARIMA model from best to worse AIC if GARCH fails to converge

```{r, eval = EVAL_GARCH_OPTION}
library(timetk)

#Settings
ERR_DIST = "std" #norm, snorm, std, sstd, ged, sged
MAX_ARIMA_P = 5
MAX_ARIMA_Q = 5
MAX_GARCH_P = 5
MAX_GARCH_Q = 5
n=0

for (i in ticker) {
  n = n + 1
  #Temporary variables
  current.symbol <- i
  #Convert to XTS object to maintain date consistencies
  df_xts <- tk_xts(all_stock,
                   select = paste(current.symbol, ".lret", sep =""),
                   date_var = "date")
  
  #Temporary dataframe to store the results for all ARIMA
  #Will not store ARIMA results that are problematic
  df_arima_results <- tibble(p=0,
                             d=0,
                             q=0,
                             AIC = Inf)
  
  

  for (p in 0:MAX_ARIMA_P) for (q in 0:MAX_ARIMA_Q) {
    if ( p == 0 && q == 0) {
      next
    }
    arimaFit = tryCatch( arima(df_xts, order=c(p, 0, q)),
                         error=function( err ) {
                           message(err)
                           return(FALSE)
                         },
                         warning=function( err ) {
                           # message(err)
                           return(FALSE)
                         } )

    if( !is.logical( arimaFit ) ) {
      df_arima_results <- df_arima_results %>%
        bind_rows(tibble(p = p,
                         d = 0,
                         q = q,
                         AIC = AIC(arimaFit)))
    } else {
      next
    }
  }
  
  #Sort the results based on the best AIC
  df_arima_results <- df_arima_results %>%
    arrange(AIC)
  
  #Fit GARCH specification
  #Move down the best AIC table if no solution can be found for all lags
  final.aic <- Inf
  m = 0
  while (final.aic == Inf & m < nrow(df_arima_results)){
    #Move down the best AIC table if no solution can be found for all lags
    m = m + 1
    final.aic <- Inf
    ARIMA_p <- df_arima_results$p[m]
    ARIMA_d <- df_arima_results$d[m]
    ARIMA_q <- df_arima_results$q[m]
    final.garchOrder <- c(0,0)
    
    for (p in 1:MAX_GARCH_P) for (q in 1:MAX_GARCH_Q) {
      print(paste("Stock =", current.symbol, 
                  "ARIMA p =", ARIMA_p,
                  "ARIMA d =", ARIMA_d,
                  "ARIMA q =", ARIMA_q,
                  "GARCH p =", p,
                  "GARCH q =", q))
      spec = ugarchspec(
        variance.model=list(model ="eGARCH",
                            #submodel = "TGARCH",
                            garchOrder=c(p,q)),
        mean.model=list(armaOrder=c(ARIMA_p,
                                    ARIMA_q),
                        include.mean=T,
                        archm = TRUE),
        distribution.model= ERR_DIST
      )
      garchFit = tryCatch(
        ugarchfit(
          spec, df_xts, solver = 'hybrid', out.sample = N_VERIFICATION
        ),
        error=function( err ) {
                             message(err)
                             return(FALSE)
                           },
        warning=function( err ) {
                             #message(err)
                             return(FALSE)
                           } )
  
      if( !is.logical( garchFit ) ) {
        current.aic <- infocriteria(garchFit)[1]
        if (current.aic < final.aic) {
          final.aic <- current.aic
          final.garchOrder <- c(p, q)
          final.garch.spec <- spec
          final.garch.fit <- garchFit
        }
      } else {
        next
      }
    }
    if (final.aic == Inf){
      print(paste("No GARCH specification found for stock",
                  current.symbol,
                  "ARIMA(",
                  p, ", ", d, ", ", q, ")"))
    }
  }
  
  #Throw an error if no GARCH specification could be found with all valid ARIMA models
  if (final.aic == Inf){
    message("ERR: No GARCH specification can be found")
  }
  
  #Store the results
  #Store the ARIMA results
  best_fit$order[[n]]$ARIMA_p = ARIMA_p
  best_fit$order[[n]]$ARIMA_d = ARIMA_d
  best_fit$order[[n]]$ARIMA_q = ARIMA_q
  #Store the GARCH results
  best_fit$spec[[n]] = final.garch.spec
  best_fit$final_fit[[n]] = final.garch.fit
  best_fit$order[[n]]$GARCH_p = final.garchOrder[1]
  best_fit$order[[n]]$GARCH_q = final.garchOrder[2]
  #Store the AICs
  best_fit$ARIMA_AIC[n] <- df_arima_results$AIC[m]
  best_fit$GARCH_AIC[n] <- final.aic
}

#Save to RDS
saveRDS(best_fit, "data/best_fit.rds")

#Delete from memory
rm(arimaFit, df_arima_results, df_xts, final.garch.fit,
   final.garch.spec, garchFit, spec, ARIMA_d, ARIMA_p, 
   ARIMA_q, current.aic,current.symbol, final.aic, final.garchOrder,
   i, m, MAX_ARIMA_P, MAX_ARIMA_Q, MAX_GARCH_P, MAX_GARCH_Q, n, p, 
   q)
```
Load
```{r}
best_fit <- readRDS("data/best_fit.rds")
```

```{r}
#Construct the uGARCHfit and uGARCHspec objects
# best_fit$spec <- map(best_fit$order, function(order){
#   ARIMA_p = order$ARIMA_p
#   ARIMA_d = order$ARIMA_d
#   ARIMA_q = order$ARIMA_q
#   GARCH_p = order$GARCH_p
#   GARCH_q = order$GARCH_q
#   
#   result <- ugarchspec(
#     variance.model=list(model ="eGARCH",
#                         #submodel = "TGARCH",
#                         garchOrder=c(GARCH_p, GARCH_q)),
#     mean.model=list(armaOrder=c(ARIMA_p, 
#                                 ARIMA_q), 
#                     include.mean=T),
#     distribution.model="sged"
#   )
#   return(result)
# })
# 
# best_fit$final_fit <- map(best_fit$spec, )
```

Get the residuals and fitted values
```{r, warning = FALSE}
df_garch_results <- all_stock_train %>%
  bind_cols(
    map(best_fit$final_fit, residuals) %>%
    set_names(paste(ticker, ".resid", sep = "")) %>%
    as_tibble() 
  ) %>%
  bind_cols(
    map(best_fit$final_fit, residuals, standardize = TRUE) %>%
    set_names(paste(ticker, ".std_resid", sep = "")) %>%
    as_tibble()
  ) %>%
  bind_cols(
    map(best_fit$final_fit, sigma) %>%
    set_names(paste(ticker, ".sigma", sep = "")) %>%
    as_tibble()
  ) %>%
  bind_cols(
    map(best_fit$final_fit, fitted) %>%
    set_names(paste(ticker, ".fitted", sep = "")) %>%
    as_tibble()
  )

ggplot(df_garch_results %>%
         select(date, ends_with(".resid")) %>%
         pivot_longer(cols = -date,
                      names_to = "symbol",
                      values_to = "residual")) +
  geom_line(aes(x=date, y = residual, color = symbol)) +
  ggtitle("Non-standardised residuals from ARIMA-GARCH")

ggplot(df_garch_results %>%
         select(date, ends_with(".std_resid")) %>%
         pivot_longer(cols = -date,
                      names_to = "symbol",
                      values_to = "std_residual")) +
  geom_line(aes(x=date, y = std_residual, color = symbol)) +
  ggtitle("Standardised residuals from ARIMA-GARCH")
```

Extract the coefficients of the standardised residual distributions, 
and append it to the best_fit df
```{r, warning= FALSE}
library(fGarch)
best_fit <- best_fit %>%
  full_join(
    df_garch_results %>%
    select(ends_with(".std_resid")) %>%
    pivot_longer(cols = everything(),
                 names_to = "symbol",
                 values_to = "std_resid") %>%
    mutate(symbol = gsub(".std_resid","",symbol)) %>%
    group_by(symbol) %>%
    summarise(std_resid.mean = mean(std_resid),
              std_resid.sd = sd(std_resid)) %>%
    bind_cols(std_resid.shape = sapply(map(best_fit$final_fit, coef), 
                                       function(x){x["shape"]})) %>%
    bind_cols(std_resid.skew = sapply(map(best_fit$final_fit, coef), 
                            function(x){x["skew"]})),
    by = "symbol")
```
```{r}
df_fitted_pdf <- df_garch_results %>%
  select(ends_with(".std_resid")) %>%
  pivot_longer(cols = everything(),
               names_to = "symbol",
               values_to = "std_resid") %>%
  mutate(symbol = gsub(".std_resid","",symbol)) %>%
  left_join(best_fit %>% select(c(symbol,
                                  std_resid.mean:std_resid.skew)),
            by = "symbol") %>%
  mutate(norm_pdf = dnorm(std_resid, 
                          mean= std_resid.mean,
                          sd = std_resid.sd))
if(ERR_DIST == "sged"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsged(std_resid, 
                            mean= std_resid.mean,
                            sd = std_resid.sd,
                            nu = std_resid.shape,
                            xi = std_resid.skew))
} else if(ERR_DIST == "sstd"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsstd(std_resid, 
                            mean= std_resid.mean,
                            sd = std_resid.sd,
                            nu = std_resid.shape,
                            xi = std_resid.skew))
} else if(ERR_DIST == "std"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dstd(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           nu = std_resid.shape))
} else if(ERR_DIST == "ged"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dged(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           nu = std_resid.shape))
} else if(ERR_DIST == "snorm"){
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = dsnorm(std_resid, 
                           mean= std_resid.mean,
                           sd = std_resid.sd,
                           xi = std_resid.skew))
} else if(ERR_DIST == "norm") {
  df_fitted_pdf <- df_fitted_pdf %>%
    mutate(std_err_pdf = norm_pdf)
}
  

ggplot(df_fitted_pdf) +
  geom_density(aes(x=std_resid, color = "Actual std resid")) +
  geom_line(aes(x=std_resid, y=norm_pdf, color = "Theoretical Normal"))+
  geom_line(aes(x=std_resid, y=std_err_pdf, color = paste("Theoretical", ERR_DIST)))+
  facet_wrap(~symbol)+
  ggtitle("Standardised Residual, theoretical distribution vs actual")
```
Using t-distribution for standardised residuals. seems that AMZN fits pretty well except for some end tail, and MSFT fits normal better for this case


```{r}
ggplot(df_fitted_pdf) +
  stat_ecdf(aes(x=std_resid, color = "actual ecdf")) +
  facet_wrap(~symbol)
```


# Out of sample forecast

```{r}
MSFT_forecast <- ugarchforecast(best_fit$final_fit[[1]], 
                                n.ahead = N_VERIFICATION)

df_forecast <- all_stock_verification %>%
  bind_cols(fitted = fitted(MSFT_forecast)) %>%
  bind_cols(sigma = sigma(MSFT_forecast)) %>%
  bind_cols(VaR = quantile(MSFT_forecast,0.05))

ggplot(df_forecast)+
  geom_line(aes(x=date, y= MSFT.lret, color = "Actual")) +
  geom_line(aes(x=date, y= fitted, color = "fitted")) +
  geom_line(aes(x=date, y= VaR, color = "5% VaR")) 

df_forecast %>% mutate(exceed_VaR = MSFT.lret < VaR) %>%
  summarise(exceed_n = sum(exceed_VaR),
            exceed_prop = sum(exceed_VaR)/N_VERIFICATION,
            exceed_prop = 0.05*N_VERIFICATION)
```
#Price estimate and VaR

```{r}
df_temp <- tibble(cum_fitted_return = cumsum(df_forecast$fitted),
                  cum_VaR = cumsum(df_forecast$VaR))
df_price_forecast <- df_forecast %>%
  bind_cols(df_temp) %>%
  mutate(predicted_price = exp(cum_fitted_return) * df_forecast$MSFT.close[1])

#To construct VaR, create N by the timelength of the data draws of the standardised error
N=100000 #Number of simulation
set.seed(100)
uRandom <- array(runif(N*N_VERIFICATION), dim = c(N, N_VERIFICATION))
uRandom <- qstd(uRandom,
                mean = 0,
                sd = best_fit$std_resid.sd,
                nu = best_fit$std_resid.shape)

#uRandom <- quantile(df_fitted_pdf$std_resid, probs = uRandom)

sigma <- matrix( rep(df_forecast$sigma, N), nrow=N, byrow=TRUE) 
eRandom <- uRandom*sigma
retRandom <- eRandom + matrix( rep(df_forecast$fitted, N), nrow=N, byrow=TRUE) 

#Calculate the price of all path
cum_retRandom <- t(apply(retRandom, MARGIN = 1, cumsum))
priceRandom <- tail(all_stock_train$MSFT.close, 1)*exp(cum_retRandom)

#Fit prediction and VaR
df_temp <- tibble(cum_fitted_return = cumsum(df_forecast$fitted),
                  cum_VaR = cumsum(df_forecast$VaR))
df_price_forecast <- df_forecast %>%
  bind_cols(df_temp) %>%
  mutate(predicted_price = exp(cum_fitted_return) * tail(all_stock_train$MSFT.close, 1)) %>%
  bind_cols(predicted_VaR5 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.05)) %>%
  bind_cols(predicted_VaR10 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.10)) %>%
  bind_cols(predicted_VaR25 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.25)) %>%
  bind_cols(predicted_VaR75 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.75)) %>%
  bind_cols(predicted_VaR90 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.90)) %>%
  bind_cols(predicted_VaR95 = apply(priceRandom, MARGIN = 2, quantile, probs = 0.95)) %>%
  bind_cols(mean_VaR = apply(priceRandom, MARGIN = 2, mean))

library(plotly)
ggplotly(ggplot(df_price_forecast) +
  geom_line(aes(x=date, y= MSFT.close, color = "Actual Price")) +
  geom_line(aes(x=date, y= predicted_price, color = "Predicted Price")) +
  geom_line(aes(x=date, y= predicted_VaR5, color = "Predicted 5% VaR")) +
  geom_line(aes(x=date, y= predicted_VaR10, color = "Predicted 10% VaR")) +
  geom_line(aes(x=date, y= predicted_VaR25, color = "Predicted 25% VaR")) +
  geom_line(aes(x=date, y= predicted_VaR75, color = "Predicted 75% VaR")) +
  geom_line(aes(x=date, y= predicted_VaR90, color = "Predicted 90% VaR")) +
  geom_line(aes(x=date, y= predicted_VaR95, color = "Predicted 95% VaR")))

ggplot(df_price_forecast) +
  geom_line(aes(x=date, y= MSFT.close, color = "Actual Price")) +
  geom_line(aes(x=date, y= predicted_price, color = "Predicted Price")) +
  geom_line(aes(x=date, y= mean_VaR, color = "mean_VaR"))

```


```{r}
a <- as_tibble(eRandom) %>% 
  select(V1:V10) %>% 
  pivot_longer(cols = everything(), 
               names_to = "time", 
               values_to = "val") %>% 
  mutate(time = as.numeric(gsub("V","",time)))

ggplot(a) + geom_density(aes(x=val, color = as.factor(time)))
```

